%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Lead Enterprise Architect} % Job title
    {Medidata Solutions} % Organization
    {NYC, USA} % Location
    {Dec. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Bridge between the business and technology, ensuring that the organization's technical solutions are
          in sync with its strategic and business goals.
        }
        \item {Responsible for architecture and design across Medidata's Study Conduct portfolio of applications.}
        \item {
          Provide guidance, mentorship, advice, and technical leadership to other architects and developers across
          cultures, countries, and time zones.
        }
      \end{cvitems}
    }
    
  \cventry
    {Lead Systems Architect}
    {}
    {}
    {Nov. 2015 - Dec. 2017}
    {
        \begin{cvitems}
          \item {
            Designed and led the implementation of a data ingestion and extraction platform, providing pluggable data 
            sources, transformations, and sinks, joining data from thousands of discrete database sources into flexible
            materializations across multiple file formats and delivery methods.
          }
          \item {
            Architected and led a team in the implementation of an scalable, sustainable, resilient system enabling the
            integration of various legacy systems spread across thousands of SIST deployments with centralized
            reference data services, running with near-zero incidents in production.
          }
          \item {
            Designed and implemented a framework for standardizing client customizations in Medidata's Electronic Data
            Capture (EDC) system, coordinating between the product management, technical services, and engineering
            teams, in order to allow customers to continue innovating in their product usage while enabling
            the engineering teams to modernize the software architecture and codebase.
          }
        \end{cvitems}
    }
    
  \cventry
    {Staff Software Engineer, Team Lead}
    {}
    {}
    {Aug. 2012 - Nov. 2015}
    {
        \begin{cvitems}
          \item {
            Re-architected an integration between two of Medidata's core systems, transforming millions of objects per
            day across disparate data models, increasing customer satisfaction and reducing toil, through defect
            resolution, system stabilization, and performance enhancements.
          }
          \item {
            Designed and developed processes and tools for integrating legacy stand-alone deployments and data with
            Medidata's core platform services.
          }
        \end{cvitems}
    }
    
  \cventry
    {Software Development Engineer in Test}
    {}
    {}
    {Jan. 2012 - Aug. 2012}
    {
        \begin{cvitems}
          \item {
            Spearheaded the implementation of continuous black-box testing for an abandoned legacy system in order to
            allow for modernization to proceed with confidence.
          }
        \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Functional Test Engineer} % Job title
    {Real-Time Technology Solutions (RTTS)} % Organization
    {NYC, USA} % Location
    {Aug. 2011 - Dec. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Architected and built out a test automation framework, designed to allow rapid implementation of use cases
          and test cases that defined the application workflow.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front-End Software Engineer} % Job title
    {General Electric} % Organization
    {NYC, USA} % Location
    {Mar. 2011 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Implemented and curated a set of medical event reporting forms, designed to facilitate and streamline
          hospital operations.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
